### 2021-02-17 README.Rmd
Fixing the build badge

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
<!-- badges: end -->

>>>>

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![Build Status](https://travis-ci.com/zabore/ppseq.svg?branch=main)](https://travis-ci.com/zabore/ppseq)
[![codecov](https://codecov.io/gh/zabore/ppseq/branch/master/graph/badge.svg)](https://codecov.io/gh/zabore/ppseq)
[![CRAN status](https://www.r-pkg.org/badges/version/ppseq)](https://CRAN.R-project.org/package=ppseq)
<!-- badges: end -->
